\myfont Implementation and evaluation of register allocation used to translate LLVM-{}- to x86-64

### 2024-01-06 article.tex
Add some of interf  func

>>>>

\begin{figure}[H]
\begin{minted}[linenos,bgcolor=LightGray]{ocaml}
let interf (params : Ll.uid list) (insns : Cfg.insn list) _ (out : S.SS.t array)
    : G.V.t S.table * G.t =
  let g = G.create () in
  let vert e t = (* .. *) in
  let vert2 t e = vert e t |> snd and vert3 e t = vert e t |> snd in
  (* add params *)
  let t = List.fold_left vert2 S.ST.empty params in
  (* connect all params *)
  let edge v1 v2 t = (* .. *) in
  let param t p1 =
    let param t p2 = if p1 <> p2 then edge p1 p2 t else t in
    List.fold_left param t params
  in
  let t = List.fold_left param t params in
  (* add all defs *)
  let setverts t s = S.SS.fold vert3 s t in
  let t = List.map (def S.SS.empty) insns |> List.fold_left setverts t in
  let defoutedges t (i, n) =
    let defs = def S.SS.empty n in
    let outedge e1 t = S.SS.fold (edge e1) out.(i) t in
    S.SS.fold outedge defs t
  in
  let t = List.mapi (fun i n -> (i, n)) insns |> List.fold_left defoutedges t in
  (t, g)
\end{minted}
\caption{Overall implementation of \texttt{dataflow}\label{fig:dataflow}}
\end{figure}
